MergeBiomarkWith10X

### 2021-11-17 MergeBiomarkWith10X/MergeBiomarkWith10X.Rmd
Additional plots added

```{r}
pseudo.biomark.T[is.na(pseudo.biomark.T)] <- 0
pseudo.biomark.T <- as.sparse(pseudo.biomark.T)
biomark.object <- CreateSeuratObject(pseudo.biomark.T, project = "biomark", assay = "RNA", meta.data = biomark.meta)
```

@@

```{r}
DefaultAssay(tech.integrated) <- "integrated"
tech.integrated <- ScaleData(tech.integrated)
tech.integrated <- RunPCA(tech.integrated, npcs = 30)
DimPlot(tech.integrated, reduction = "pca", group.by = "orig.ident", pt.size = 2)
```

>>>>

```{r}
pseudo.biomark.T[is.na(pseudo.biomark.T)] <- 0
pseudo.biomark.T <- as.sparse(pseudo.biomark.T)
biomark.object <- CreateSeuratObject(pseudo.biomark.T, project = "biomark", assay = "RNA", meta.data = biomark.meta)
```
## Thought experiment
```{r}
dbiomark.T <- data.table::transpose(dbiomark.data)
dbiomark.object <- CreateSeuratObject(dbiomark.T, project = "biomark", assay = "RNA", meta.data = biomark.meta)
```

@@

```{r}
DefaultAssay(tech.integrated) <- "integrated"
tech.integrated <- ScaleData(tech.integrated)
tech.integrated <- RunPCA(tech.integrated, npcs = 30)
DimPlot(tech.integrated, reduction = "pca", group.by = "orig.ident", pt.size = 2, cols = c("red", "black"))

png(filename = paste0(projectName, "anchored_PCA.png"), height = 800, width = 800, bg = "transparent")
DimPlot(tech.integrated, reduction = "pca", group.by = "orig.ident", pt.size = 2, cols = c("red", "black"), combine = FALSE)
dev.off()
```
